---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#VSdecomp: Variance and Skewness Decomposition

An R package that provides decomposition methods for the skewness or the variance of a variable (e.g., wage). By breaking distribution moments into independent components, users can analyze changes in distributions across time or between groups.
          

##Installation

Currently, only the GitHub version is available through:
```{r, message=FALSE, eval=FALSE}
#install.packages("devtools")
devtools::install_github("eladg9/VSdecomp/r-package")
```

##Usage Example

```{r, message=FALSE, eval=FALSE}
library(VSdecomp)
#generate data
n <- 1000
men <- rbinom(n, 1, 0.5)
black <- rbinom(n, 1, 0.5)
year <- c(rep(2019, n/2), rep(2020, n/2))
rwage <- function(x){
  m <- x[1]; b <- x[2]; y <- x[3];
  exp(rnorm(1, mean = 1*m + 1*b, sd = 1 + 2020 - y))
}
dat <- data.frame(men, black, year)
dat$wage <- apply(dat, 1, rwage)
#skewness decomposition by one variable:
variable <- as.matrix(dat$men)
decomp_by_gender <- vs_decomp(y = dat$wage, X = variable,
                              moment = "skew", year = dat$year)
summary(decomp_by_gender)
plot(decomp_by_gender)

#skewness decomposition by more than one variable (a.k.a linear skewness decomposition):
#first we need to decompose wage into its linear components
#(check ?linear_projection )
wage_linear_comp <- linear_projection(y = "wage", 
                                      X.list = list("men", "black"),
                                      data = dat)
```

##References


